\acknowledgementtext{%
The three years of my PhD have been a thrilling period of learning, both in terms of scientific knowledge and personal growth. This journey allowed me to explore exciting research directions, travel to various parts of the world, and, most significantly, meet a lot of people. I want to thank all of my colleagues at FAU Erlangen-Nürnberg for making the experience at the Chair of Applied Mathematics what it was. I especially want to express my gratitude to the following people:
%
\begin{itemize}
\item Martin Burger for granting me a student assistant position back in 2018, even though I hail from the Upper Palatinate. Since then, I have relished the unique blend of freedom to express myself, coupled with dependable support whenever required.
%
\item Daniel Tenbrinck for being the heart of our former chair at FAU, serving as the driving force behind every important social event, being an inherently helpful person, setting up the GPU servers, and, most importantly, for winning the Best Teaching Award in 2021 and giving me credit for it. During my time at FAU, we worked a lot together, especially on teaching-related topics, which always turned out to be a great success. I miss the idea of preparing lectures together. I hope we can collaborate in the future, and I am sure we'll see each other whenever time allows.
%
\item Leon Bungert for basically co-supervising my PhD and for teaching me a lot about mathematics, culture, cooking, and colorful shirts. Given the wealth of experiences we've shared during the last four years, it's not easy to express all of this within a few lines. Apart from our collaborations on an academic level, I want to thank you for being a very close friend.
%
\item Antonio Esposito for being a really nice guy, greatly improving my fake Italian accent, and, most of all, for being part of our group. I was really sad when you left for Oxford, and I hope to meet you again soon.
%
\item Alex Rossi for sparking my interest in patches, teaching me how to dress austere and introducing me to authentic Italian desserts. I think you're a great guy, and I've always loved hanging out with you.
%
\item Lukas Weigand for introducing me to the green book, helping with the exercise sheets for numerics, and teaching me a lot about gradient flows. I look forward to working together with you in the future.
%
\item Lorenz Kuger for sharing the office with me for a long time, despite being the best-organized PhD student I know, not getting too annoyed about every non-work related activity I started in the office, and for being a great colleague. Transitioning to Hamburg was especially easy thanks to your pioneering a lot of bureaucratic ground.
%
\item All the other colleagues I spent time with in Erlangen, or met around the world, namely:
\begin{itemize}
\item Philipp Wacker for making me aware of the field of statistics,
\item Jannik Hausladen for helping me a lot with our MRI project,
\item Alexander Prechtl for always bringing the servers back to life (together with Daniel), when I crashed them,
\item Jeff Calder for collaborating with Leon and me on Lipschitz leaning and writing that very nice graph learning package, which made everything a lot easier,
\item Nicolás García Trillos for organizing a nice mini-symposium together with me in Tokyo,
\item and Konstantin Riedl for being yet another great mathematician from the Upper Palatinate.
\end{itemize}
%
\item All my other colleagues and short-time office mates that just recently joined the Burger group, with whom I am now starting a new chapter in Hamburg.
%
\item Astrid Bigott for always being understanding of my difficult relationship with bureaucracy and for finding all the mistakes I ever made in any kind of form.
%
\item My proofreaders Leon, Norman, Martin, and Samira.
%
\item My parents for always showing me affection and supporting me unconditionally. Although I am not always physically there, I will never lose my connection to home. Also, I want to extend my thanks to Miezer for always letting me use his pictures for imaging purposes.
%
%
%
%
%
%
\item Samira Kabri for teaching me about FNOs. 
\end{itemize}
}